---
title: "Trump tweet analysis by dplyr"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

# Source
* Author: The case is written by David Robinson, author of the book "R for text mining", author of library tidytext, data scientist at StackOverFlow.
* Link of github: https://github.com/dgrtwo/dgrtwo.github.com/blob/master/_R/2016-08-09-trump-tweets.Rmd
* Link of the article: http://varianceexplained.org/r/trump-tweets/


# Load and clean data

```{r}
library(tidyverse)
options(stringsAsFactors = F)
```

# Loading data
```{r}
load(url("http://varianceexplained.org/files/trump_tweets_df.rda"))
dim(trump_tweets_df)
names(trump_tweets_df)
trump_tweets_df %>%
  select(id, text, created, favoriteCount,  retweetCount, statusSource) %>% View
```




# Cleaning data
- Extracting publishing device of tweets
```{r}
library(tidyr) # tidyr::extract()
library(stringr) # stringr::str_replace
trump_tweets_df$statusSource[1]
tweets <- trump_tweets_df %>%
    select(id, statusSource, text, created) %>%
    # mutate(source = str_replace(statusSource, 
    #                             ".*Twitter for (.*?)<.*", "\\1")) %>%
    # mutate(source = str_extract(statusSource, 'Twitter for (.*?)<')) %>% View
    extract(statusSource, "source", "Twitter for (.*?)<") %>%
    filter(source %in% c("iPhone", "Android"))

# Using stringr::str_replace() to mutate a new source variable, replacing tidyr::

# str(tweets)
```


# Vis: Hour by tweet percentage
- Converting timezone
- Plotting number of tweets by hour

```{r}
library(lubridate)
library(scales)
tweets %>%
    count(source, hour = hour(with_tz(created, "EST"))) %>%
    # group_by(source) %>%
    mutate(percent = n / sum(n)) %>% 
    # ungroup() %>%
    ggplot() +
    aes(hour, percent, color = source) +
    geom_line(size = 1) +
    scale_color_manual(name = "", labels = c("Android", "iPhone"),
                       values = c("royalblue", "tomato")) +
    scale_y_continuous(labels = percent_format()) +
    labs(x = "Hour of day (EST)",
         y = "% of tweets",
         color = "") + 
    bbplot::bbc_style()
```


# With Pictures or Not
- Filtering out tweets starting with "
- Mutating new variable `picture` to indicate whether text has picture or not?
- Counting `source` by `picture`
- Plotting bar chart to compare difference between sources.

```{r}
library(stringr)
tweets %>%
    filter(!str_detect(text, '^"')) %>%
    mutate(picture = if_else(str_detect(text, "t.co"),
                             "Picture/link", "No picture/link")) %>%
    count(source, picture) %>%
    ggplot() + 
    aes(source, n, fill = picture) + 
    geom_col(position="stack") + 
    scale_fill_manual(name = "", labels = c("Picture/link", "No picture/link"),
                      values = c("royalblue", "gold")) + 
    labs(x = "", y = "Number of tweets", fill = "") + 
    bbplot::bbc_style()

devtools::install_github('bbc/bbplot')

# ggplot(tweet_picture_counts, aes(source, n, fill = picture)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   
```



# Comparison of words
```{r}
library(tidytext)	# unnest_tokens()
library(stringr)	# str_detect(), str_replace_all()

# View(test)

# stop_words$word

tweet_words <- tweets %>%
    filter(!str_detect(text, '^"')) %>%
    mutate(text = str_replace_all(text, "https://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
    # unnest_tokens(word, text) %>%
    # unnest_tokens(word, text, token = "regex", pattern = "[^A-Za-z\\d#@']") %>%
    mutate(word = str_split(text, " ")) %>% 
    select(id, text, word, everything()) %>%
    unnest(word) %>%
    filter(!word %in% stop_words$word,
           str_detect(word, "[a-z]"))
# View(tweet_words)
```


```{r}
tweet_words %>%
    count(word, sort = TRUE) %>%
    head(20) %>%
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col(fill = "limegreen") +
    ylab("Occurrences") +
    coord_flip() + 
    bbplot::bbc_style()

```



# words frequency by different devices
```{r}
test <- tweet_words %>%
    count(word, source) %>%
    filter(n >= 5) %>%
    spread(source, n, fill = 0)
# View(test)

word_by_source <- tweet_words %>%
    count(word, source) %>%
    filter(n >= 5) %>%
    spread(source, n, fill = 0) %>%
    ungroup()

sum(word_by_source$iPhone)
sum(word_by_source$Android)

android_iphone_ratios <- word_by_source %>%
    mutate(iPhone = (iPhone+1)/sum(iPhone+1)) %>%
    mutate(Android = (Android+1)/sum(Android+1)) %>%
    # mutate_at(.cols = vars(iPhone, Android),
    # .funs = funs((. + 1) / sum(. + 1))) %>%
    mutate(logratio = log2(Android / iPhone)) %>%
    arrange(desc(logratio))
```

## visualizing ratio
```{r}
android_iphone_ratios %>%
    mutate(word = reorder(word, logratio)) %>%
    ggplot() + 
    aes(word, logratio, fill=logratio < 0) + 
    geom_col() + 
    coord_flip()

library(bbplot)
plot <- android_iphone_ratios %>%
    group_by(logratio > 0) %>%
    top_n(10, abs(logratio)) %>%
    ungroup() %>%
    mutate(word = reorder(word, logratio)) %>%
    ggplot(aes(word, logratio, fill = logratio < 0)) +
    geom_col() +
    coord_flip() +
    ylab("Android / iPhone log ratio") +
    scale_fill_manual(name = "", labels = c("Android", "iPhone"),
                      values = c("royalblue", "gold")) + 
    bbc_style()
finalise_plot(plot,
    source = "Source: ONS",
    save_filepath = "filename_that_my_plot_should_be_saved_to-nc.png",
    width_pixels = 800,
    height_pixels = 600)
```


```{r}
class(android_iphone_ratios$word)
```

```{r}
old_str <- "user_id=11066"

str_sub(hw, 1, 6)
str_sub(hw, end = 6)
str_sub(hw, 9, 14)
str_sub(hw, 9)
str_sub(hw, c(1, 8), c(6, 14))
mutate(new_str = as.numeric(str_sub(old_str, 9)))
```


